\thesistitle

### 2019-08-20 sections/conclusion.tex
Conclusion

We defined three aspects as part of the context of a clone: relation, location and contents. Regarding relations, we found that 37\% of clones are found in the same class. 24\% of clones are in the same inheritance hierarchy. Another 24\% of clones are unrelated. The final 7\% of clones have the same interface. Regarding where a clone is found, 78\% of clones is found at method-level of which 77\% is found in the body of a method or constructor. Because of this, the ``Extract Method'' refactoring method is most suitable to refactor most clones.

We built a tool that can automatically apply refactorings to 28\% of clones in our corpus using the ``Extract Method'' refactoring technique. The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, for instance when code outside a method is part of a clone.

We measured the effect of clone refactoring on the volume, cyclomatic complexity, duplication and method parameters metrics of the codebase. We measured these metrics before- and after each clone class that was refactored to determine the impact of each refactoring on system maintainability. We found that the most prominent factor influencing maintainability is the size of the clone. For our dataset, at a clone volume of 29 tokens per clone instance the average clone refactoring improved system maintainability. Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data. We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.

>>>>

To determine which refactoring techniques are most suitable to refactor most clones, we analyzed their context. We measured the \textbf{relation} through inheritance of clone instances in a clone class. In our corpus, we found that 37\% of clones are found in the same class. 24\% of clones are in the same inheritance hierarchy. Another 24\% of clones are unrelated. The final 7\% of clones have the same interface. We also looked at the \textbf{location} of clones: 78\% of clones is found at method-level of which 77\% is found in the body of a method or constructor. Because of this, the ``Extract Method'' refactoring method is most suitable to refactor most clones.

We built a tool that can automatically apply refactorings to 28\% of clones in our corpus using the ``Extract Method'' refactoring technique. The main reason our tool could not refactor all clones is that many clones span certain statements that obstruct method extraction, for instance when code outside the method body is part of a clone.

We measured the effect of clone refactoring on the volume, cyclomatic complexity, number of parameters and duplication metrics of the codebase. We measured these metrics before- and after each clone class that was refactored to determine the impact of each refactoring on system maintainability. We found that the most prominent factor influencing maintainability is the size of the clone. For our dataset, at a clone volume of 29 tokens per clone instance the average clone refactoring improved system maintainability. Another factor with a major impact on maintainability is the number of parameters that the extracted method requires to get all required data. We noticed that the inheritance relation of the clone and the return value of the extracted method has only a minor impact on system maintainability.
